The Hydrogen Epoch of Reionization Array Dish: Characterization with Electromagnetic Simulations

### 2016-01-13 DishSimulations/paper/DishSimulationsPaper_v1.tex
small change to paper

In Fig.~\ref{fig:SignalCompare} we compare the levels of the LST averaged foregrounds and cleaning residuals with and without the chromaticity of the dish for the redshifts between $7$ and $10.5$. Between the redshifts of $7$ and $8.5$, the residuals with and without the chromaticity of the dish drop below the level of the 21\,cm signal below $k \approx 0.12-0.15$\,$h$Mpc$^{-1}$. At $z = 8.5$, at the band center, where we found the reflections to be most severe, the beam chromaticity extends foreground contamination in excess of the signal out to $k \approx 0.22$\,$h$Mpc$^{-1}$. As we move to progressively higher redshift, the fixed frequency interval corresponding to $\Delta z = 0.5$ decreases as $(1+z)^{-2}$ while the foregrounds themselves also become brighter. The power spectrum we use here also has also reached its maximum $z=8.5$ where $50\%$ reionization takes place. For these reasons, the $k_\parallel$ at which the foregrounds with and without beam chromaticity fall below the signal increase with redshift, falling below the between $k=0.17$ and $k=0.22$\,$h$Mpc$^{-1}$ out to $z=10.5$.

>>>>

Computing the power spectrum, we inspect
